paper_figures.Rmd

### 2018-02-13 Source/Figures/paper_figures.Rmd
paper figures minor update
Update figures

local_base_directory <- "/home/ignatius/PostDoc/2016/Triplet_Motifs/Source"
source( file.path( local_base_directory, "./Common/parameters_file.R") ) 
source( file.path ( source_directory_common, 'count_triplet_motifs_helper.R'))
source( file.path ( source_directory, './Figures/paper_figures_helper.R') )

@@

stat_test_result_random_edges <- stat_test_result_random_edges %>%
								 dplyr::mutate( motif_type = factor(motif_type, levels = rev(motif_types_sorted_by_counts_desc) ), 
								 			   is_significant_star = ifelse( is_significant==1, "*", "")  )

>>>>

local_base_directory <- "/home/ignatius/PostDoc/2017/Triplet_Motifs/Source"
source( file.path( local_base_directory, "./Common/parameters_file.R") ) 
source( file.path ( source_directory_common, 'count_triplet_motifs_helper.R'))
source( file.path ( source_directory, './Figures/paper_figures_helper.R') )

@@
